---
title: "TripAdvisor"
author: "Aidi Bian"
date: "2/24/2019"
output: html_document
---

Load libraries
```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
```

```{r}
# read original data set
activity<-read.csv("activity_data.csv", header=TRUE)
hotel<-read.csv("hotel_data.csv", header=TRUE)
```

Prep data for clustering
- cluster by "user_action" variable
- count "clicks_action" by user id
- spread "clicks_action" and counts
- end goal: one row per user_id

```{r}
library(lubridate)
DF <- left_join(activity,hotel,by="hotel_id")
DF$date<-as_datetime(DF$date)
training1<-filter(DF, date<=as_datetime("2019-1-20"))
testing1<-filter(DF, date>as_datetime("2019-1-20"))
```


Import User Activity Data

```{r}
U.df <- training1 %>% group_by(user_id, user_action) %>% count() # count user_action
U.df2 <- spread(U.df, user_action, n, fill=0) # spread user_action
colnames(U.df2) <- c("user_id", "click_booking", "click_hotel_website", "click_price", "click_view") # rename columns
#actClick2[duplicated(actClick2$user_id),] # check duplicate rows
U.df3 <- ungroup(U.df2) %>% select(-user_id)
```

More Pre-Processing Steps - Scale Data
```{r}
U.df3 <- scale(U.df3)
```

Elbow Plot
Source: https://www.r-bloggers.com/finding-optimal-number-of-clusters/

```{r}
#Elbow Method for finding the optimal number of clusters
set.seed(123)
# Compute and plot wss for k = 2 to k = 15.
k.max <- 15
data <- df3
wss <- sapply(1:k.max, 
              function(k){kmeans(data, k, nstart=50,iter.max = 15 )$tot.withinss})
wss
plot(1:k.max, wss,
     type="b", pch = 19, frame = FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares")
```

Bayesian Inference Criterion for k means
Source: https://www.r-bloggers.com/finding-optimal-number-of-clusters/

```{r}
library(mclust)
d_clust <- Mclust(as.matrix(df3), G=1:15, 
                  modelNames = mclust.options("emModelNames"))
d_clust$BIC
plot(d_clust)
```

# Build Recommender System models with different clusterings

K-Means
```{r}
U.fit <- kmeans(U.df3, 5)
``` 

Data with fitted cluster
```{r}
U.df4 <- data.frame(U.df3, U.fit$cluster, U.df2$user_id)
U.df4$total_clicks <- U.df4$click_booking + U.df4$click_hotel_website + U.df4$click_price
# df4[!complete.cases(df4),] # check duplicates
U.df5 <- select(U.df4, 5:7)
uh <- select(activity, user_id, hotel_id)
names(U.df5) <- c("ucluster", "user_id", "total_clicks")
U.df6<-left_join(U.df5, uh, by="user_id")
```


```{r}
H.df<-select(hotel, c("hotel_id", "star_rating","bubble_score", "review_count"))
H.df<-H.df[!duplicated(H.df$hotel_id),]
rownames(H.df)<-H.df$hotel_id
H.df1<-H.df
H.df1<-as.matrix(H.df1)
H.df1[,-1]<-scale(H.df1[,-1])
H.df1[is.na(H.df1)]<-0

#Elbow Method for finding the optimal number of clusters
set.seed(234)
# Compute and plot wss for k = 2 to k = 15.
k.max <- 15
data <- H.df1
wss <- sapply(1:k.max,
            function(k){kmeans(data, k, nstart=50,iter.max = 15 )$tot.withinss})
wss
plot(1:k.max, wss,
   type="b", pch = 19, frame = FALSE,
   xlab="Number of clusters K",
   ylab="Total within-clusters sum of squares")
```

```{r}
H.fit<-kmeans(H.df1[,-1], 3)
H.df2 <- data.frame(H.df1, H.fit$cluster)
names(H.df2)<-c("hotel_id","star_rating","bubble_score", "review_count", "hcluster")
```


```{r}
# merge the two clusered dataset
df1<-left_join(U.df6, H.df2, by="hotel_id")
df2<-select(df1,ucluster,hcluster,total_clicks)
df3<- df2 %>% group_by(ucluster,hcluster) %>% summarise(total_clicks=sum(total_clicks))
df4<-spread(df3,hcluster,total_clicks)
rownames(df4) <- df4$ucluster
df4$ucluster<-NULL
```

```{r}
library(lsa)
df4<-as.matrix(df4)
H.SIM <- cosine(df4)
diag(H.SIM)<-NA
```

```{r}
# test the similarity matrix with testing set
a <- matrix(, nrow = 1, ncol=nrow(testing1))
h <- select(H.df2,hotel_id,hcluster)
testing1<-left_join(testing1, h, by="hotel_id")

for (i in 1:nrow(testing1)) {
  a[,i] <- head(rownames(H.SIM[order(H.SIM[testing1[i,15],], decreasing=TRUE),]),1)
}

u <- select(U.df6,user_id,ucluster)
testing1<-left_join(testing1, u, by="user_id")

testing1$hsim <- t(a)
for (i in 1:nrow(testing1)) {
  testing1$rec_user[i] <- which(df4[,testing1$hsim[i]]==max(df4[,testing1$hsim[i]]))
}

table(testing1$rec_user,testing1$ucluster)
```




